% MARK: Dedication
\begin{dedication} \noindent

    \vspace{\stretch{1}}

    In loving memory of my grandpa and oupa,

    \vspace{\baselineskip}

    \textbf{Boyd McGowan Fichardt Cooper} \\
    $1942 - 2021$

    \vspace{\baselineskip}

    \textbf{Jacobus Pieter `Koos' van der Merwe} \\
    $1947 - 2024$

    \vspace{\stretch{2}}

\end{dedication}

% MARK: Acknowledgements
\begin{acknowledgements}

    \parskip 0.8\baselineskip

    I hereby acknowledge and express my sincere gratitude to the following parties for their invaluable support and contributions.

    Firstly, I would like to thank my supervisor, Prof. Brian van Soelen.
    Your guidance, patience, and willingness to put up with all of my `Dear sir' emails is greatly appreciated.

    I acknowledge the financial support from the Department of Physics, UFS, whose funding made this project possible.
    To my colleagues and friends at UFS, notably Natalie and Joleen, thank you for your support and encouragement, without which this project would not have been as fun or enjoyable as it was.
    To Daniel and J.P., I can't believe we made it this far, but I'm glad we did.
    
    I would also like to acknowledge the \glsxtrshort{SAAO}/\glsxtrshort{SALT} teams for making this project possible, notably Dr.~Dani\`el Groenewald for her instruction in getting the \polsalt\ software running.
    
    
    For their continuous love and support I thank my parents, Samantha and Juan Barnard, Andre and Sarah van der Merwe, as well as my brother Jacob van der Merwe.

    Thank you, too, to those who may as well be family, the van der Walt's, and the Litch's.
    You have been a constant source of support and love, and I am grateful for you all.
    
    Finally, to my friends, your unfailing friendships have been anchors keeping me sane and smiling.
    Thank you.
    To Monica, thank you for being the year-long push I needed to get this done.
    Truly, I would not have finished this it weren't for you.
    To Johan\'e, you have shown me how kind and caring a person can be, and I am proud to call you friend.
    To Wian, thank you for being weirder than me and showing me that there's a world outside of university.
    To Candes, thank you for always being a great friend, even when I disappear for months at a time.

    
    \vspace*{\fill}
    \begin{flushright}
        ``Oh, and in case I don't see ya,

        good afternoon,

        good evening,

        and goodnight.''\!\!

        \vspace{\baselineskip}

        $-$ \textit{Truman Burbank}

    \end{flushright}

\end{acknowledgements}
